### 2016-12-10 paper/evaluation.tex
updated rq1

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from
Github\Jbc{Remember to update the previous sentence after updating the
subject section}. We are interested in understanding the prevalence
of long test runs, the main sources of cost, and how do developers
explore parallelism to improve execution performance. More
specifically, we pose the following research questions:

@@

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}).  Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group: on the left side, the pie chart
reports the results enforcing sequential execution; on the right side,
the results for the default execution.  Results indicate that a
relatively high number of projects from the sample set (\ie, 17\%)
requires at least five minutes to execute. The longest execution takes
\Fix{x} to finish. It is important to mention that
Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
time: some tests may finish early due to a failure since the subjects
were tested in a potentially unstable revision.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.48\textwidth]{plots/piechart-timecost.pdf}
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
    5m$), and long execution ($5m \leq t$).  \Fix{On the left side, results from
    sequential execution}; on the right side, results from default execution.}
\end{figure}

Considering the groups \emph{medium} and \emph{long} (\Fix{X} subjects), we
investigated the relationship between the number of tests cases and the time
cost from subjects. \Fix{Explain what is correlation and how it is computed.}
\Fix{elaborate: As expected, Figure~\ref{fig:scatters} reveals that the number
of tests cases are not related to the elapsed time.  \Fix{explain briefly what
dominates a test execution/types of tests}.Results indicate that
\Fix{...conclusion...}.}

\begin{figure}[h!]%
    \centering
    \Comment{scatter top, scatter bottom, legend r-value regression}
    \caption{\Fix{...use minutes instead of secs...}}%
    \label{fig:scatters}%
\end{figure}

@@

To evaluate how often developers use low-level parallelism, we
considered 216 Maven projects and analyzed \Fix{x} configurations
files. \Fix{For each subject, we parsed all \emph{pom.xml} files from the
project (including submodules) and searched for all \emph{surefire}
settings on each XML file. Figure \Fix{...} illustrates how a
developer can explore parallelism via Surefire settings.}

\begin{figure}[h!]
   \centering
   \caption{\Fix{...}}
\end{figure}

>>>>

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from Github. We are
interested in understanding the prevalence of long test runs, the main
sources of cost, and how do developers explore parallelism to improve
execution performance. More specifically, we pose the following
research questions:

@@

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}). Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group and Figure~\ref{fig:boxplots-time}
shows the distribution of elapsed time for each group (boxplots).

\begin{figure}[h!]
    \centering
    \begin{minipage}{2in}%
    \includegraphics[width=\textwidth]{plots/piechart-timecost.pdf}
    \end{minipage}%
    \caption{\label{fig:piechart-time} Subjects grouped by elapsed time on test
    execution ($t$): short execution ($t < 1m$), medium execution ($1m \leq t <
    5m$), and long execution ($5m \leq t$).}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{minipage}{2.5in}%
    \includegraphics[width=\textwidth]{plots/boxplots-timecost.pdf}
    \end{minipage}%
    \caption{\label{fig:boxplots-time} Distribution of time execution
    per group. Outliers from \emph{Long} are ignored for better
    readability.}
\end{figure}

Results indicate that a relatively high number of projects from the
sample set (\ie, 29,2\%) requires at least five minutes to execute.
The boxplot for the \emph{long} group reveals \Fix{dissect the
boxplot: skewness, median, IQR}. \Fix{Discuss outliers from Long
group}.  It is important to mention that
Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
time: some tests may finish early due to a failure since the subjects
were tested in a potentially unstable revision.

@@

\Fix{To evaluate how often developers use low-level parallelism, we
considered 216 Maven projects and analyzed \Fix{x} configurations
files. For each subject, we parsed all \emph{pom.xml} files from the
project (including submodules) and searched for all \emph{surefire}
settings on each XML file. Figure \Fix{...} illustrates how a
developer can explore parallelism via Surefire settings.}
